---
title: "June Granada"
output: html_notebook
---


```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
```

_CS_individuals_jun2023._ It includes Dimensions data of researchers who started publishing from 2007 onwards (this is the earliest date for which we have topics), have been active for 10 years (published at least 1 paper in 10 different years), excluding the 25 most productive percentile of researchers.

```{r}
colsn <- 
c('Researcher_id','first_year','active_years','pub_year','pub_id','country_code',
  'author_seq','is_corresponding_author','cluster_id1','LR_main_field')

df <- read_delim('../../data/CS_individuals_jun23.csv',delim = ';',col_names = colsn)
```

## dataset exploration

```{r}
df
```

```{r}
df$pub_id %>% unique() %>% length()
```
```{r}
df$Researcher_id %>% unique() %>% length()
```

```{r}
table(df$active_years)
```

```{r}
df %>% 
  ggplot(aes(first_year)) +
  geom_histogram()
```


```{r}
df %>% 
  ggplot(aes(first_year,active_years)) +
  geom_hex()
```
## Productivity

```{r}
df %>% 
  group_by(Researcher_id) %>% 
  summarise(first_year = unique(first_year),
            n_papers = length(unique(pub_id))) %>% 
  group_by(first_year) %>% 
  summarise(n_papers=mean(n_papers))
```
```{r}
df %>% 
  group_by(Researcher_id) %>% 
  summarise(active_years = unique(active_years),
            n_papers = length(unique(pub_id))) %>% 
  group_by(active_years) %>% 
  summarise(n_author=length(unique(Researcher_id)))
```


```{r}
df %>% 
  group_by(Researcher_id) %>% 
  summarise(active_years = unique(active_years),
            n_papers = length(unique(pub_id))) %>% 
  group_by(active_years) %>% 
  summarise(n_papers=mean(n_papers))
```

```{r}
df %>% 
  group_by(Researcher_id) %>% 
  summarise(LR_main_field = unique(LR_main_field),
            n_papers = length(unique(pub_id))) %>% 
  group_by(LR_main_field) %>% 
  summarise(n_papers=mean(n_papers))
```
## Topics

```{r}
df_authors <- df %>% 
  group_by(Researcher_id) %>% 
  summarise(first_year = unique(first_year),
            active_years = unique(active_years),
            country_code = unique(country_code),
            mobile = length(unique(country_code))>1,
            n_papers = length(unique(pub_id)),
            n_LR_main_field = length(unique(LR_main_field)),
            ntopics = length(unique(cluster_id1)))
```


```{r}
df_authors
```
Mobile researchers

```{r}
prop_mobile <- df %>% 
  group_by(Researcher_id) %>% 
  summarise(mobile = length(unique(country_code))>1) %>% 
  pull(mobile) %>% table()

prop_mobile/sum(prop_mobile)
```

__doubt__ why we have 45% of authors with more than one country?

```{r}
df_authors %>% 
  group_by(n_papers) %>% 
  summarise(n_authors = n(),
            prop_mobile = mean(mobile),
            avg_n_fields =mean(n_LR_main_field/n_papers),
            avg_n_topics =mean(ntopics/n_papers))
```


```{r}
df_authors %>% 
  group_by(n_papers) %>% 
  summarise(n_authors = n(),
            avg_field_per_paper =mean(n_LR_main_field/n_papers),
            avg_topics_per_paper =mean(ntopics/n_papers)) %>% 
  ggplot(aes(n_papers, avg_topics_per_paper, fill = n_authors))+
  geom_col()
```

Authors with more papers are also more focused on their topics. For auhtors with more than 50 papers 0.25 means that they work on a new topic every 4 papers. While for authors with ~ 10 papers 0.5 means that they work on a new topic every 2 papers

## countries

```{r}
large_countries <- table(df_authors$country_code)[table(df_authors$country_code)>1000]%>% names
```


```{r}
df_authors %>% 
  filter(country_code %in% c('AR','CA','CH','ES','GB','JP','ZA','US')) %>% 
  group_by(n_papers,country_code) %>% 
  summarise(n_authors = n(),
            avg_field_per_paper =mean(n_LR_main_field/n_papers),
            avg_topics_per_paper =mean(ntopics/n_papers)) %>% 
  ggplot(aes(n_papers, avg_topics_per_paper, fill = n_authors))+
  geom_col()+
  facet_wrap(country_code~.)
```
Seems to be stable across countries. Taking authors with more than 10 papers might give us a more stable group

```{r fig.width=10}

df_authors %>% 
  filter(country_code %in% large_countries,
         n_papers>10) %>% 
  group_by(country_code) %>% 
  summarise(n_authors = n(),
            avg_field_per_paper =mean(n_LR_main_field/n_papers),
            avg_topics_per_paper =mean(ntopics/n_papers)) %>% 
  mutate(country_code = fct_reorder(country_code,avg_topics_per_paper)) %>% 
  ggplot(aes(country_code, avg_topics_per_paper, fill = country_code))+
  geom_col()+
  theme(legend.position = 'none')
```

## authorship

```{r}
single_papers <- df %>% 
  group_by(pub_id) %>% 
  summarise(author_seq = max(author_seq)) %>% 
  filter(author_seq==1)
```


```{r}
single_authors <- df %>% 
  filter(pub_id%in% single_papers$pub_id) %>% 
  group_by(Researcher_id) %>% 
  summarise(first_year = unique(first_year),
            active_years = unique(active_years),
            country_code = unique(country_code),
            n_papers = length(unique(pub_id)),
            n_LR_main_field = length(unique(LR_main_field)),
            ntopics = length(unique(cluster_id1))) %>% 
  mutate(authorship= 'single authors')

corr_authors <- df %>% 
  filter(!pub_id%in% single_papers$pub_id, is_corresponding_author==1) %>% 
  group_by(Researcher_id) %>% 
  summarise(first_year = unique(first_year),
            active_years = unique(active_years),
            country_code = unique(country_code),
            n_papers = length(unique(pub_id)),
            n_LR_main_field = length(unique(LR_main_field)),
            ntopics = length(unique(cluster_id1))) %>% 
  mutate(authorship= 'corresponding authors')

non_corr_authors <- df %>% 
  filter(!pub_id%in% single_papers$pub_id, is_corresponding_author==0) %>% 
  group_by(Researcher_id) %>% 
  summarise(first_year = unique(first_year),
            active_years = unique(active_years),
            country_code = unique(country_code),
            n_papers = length(unique(pub_id)),
            n_LR_main_field = length(unique(LR_main_field)),
            ntopics = length(unique(cluster_id1))) %>% 
  mutate(authorship= 'non corresponding authors')
```



```{r}
bind_rows(list(single_authors,corr_authors,non_corr_authors)) %>% 
  group_by(authorship) %>% 
  summarise(n_authors = n(),
            avg_field_per_paper =mean(n_LR_main_field/n_papers),
            avg_topics_per_paper =mean(ntopics/n_papers)) %>% 
  ggplot(aes(authorship, avg_topics_per_paper, fill = authorship))+
  geom_col()
```

## Mobility

```{r}
df_authors %>% 
  group_by(mobile) %>% 
  summarise(n_authors = n(),
            avg_field_per_paper =mean(n_LR_main_field/n_papers),
            avg_topics_per_paper =mean(ntopics/n_papers)) %>% 
  ggplot(aes(mobile, avg_topics_per_paper, fill = mobile))+
  geom_col()
```

Mobile researchers are more focused on their topics




